Actuator line modeling of vertical-axis turbines

### 2016-05-12 paper.tex
Remove some unnecessary software details

OpenFOAM and turbinesFoam are written in the C++ programming language, which
follows the object oriented programming paradigm. This characteristic helped
modularize the ALM code for increased readability and reuse. In turbinesFoam, a
turbine is a software object that is composed of actuator line objects, which
themselves are composed of actuator line element objects. Structuring the code
this way allows isolation and reuse of the functionality of individual
components. For example, the actuator line object was written such that is could
be used outside the turbine context to ensure it produces the correct forcing,
without adding the complexity of rotation, other actuator lines, etc. that would
be present in a turbine rotor. The very same actuator line objects can be used
in both axial-flow and cross-flow rotors, without having to copy code from one
to the other. In contrast, the actuator line model in SOWFA uses a single
software object to represent an entire array of turbines, which necessitates
iterating through many nested lists down to the element level, which can be
confusing to read.

OpenFOAM's data structures are designed to be inherently parallel via message
passing interface (MPI). By working within the library infrastructure the ALM
code was easily parallelized, which will facilitate its deployment on high
performance computing clusters for large flow simulations.

Since all applications are run from a command line and all input data is text
based, automation and integration with other tools is relatively
straightforward. Future enhancements could include coupling with software for
generating static foil data, e.g., XFOIL~\cite{Drela1989} or other OpenFOAM
solvers, turbine controller models, structural analysis codes, and optimization
tools, e.g., SNL's DAKOTA \cite{AdamsBaumanBohnhoffEtAl2009} or
OpenMDAO~\cite{Gray2010}, for both individual turbines and array layouts.

>>>>

OpenFOAM and turbinesFoam are written in the C++ programming language, which
follows the object oriented programming paradigm. This characteristic helped
modularize the ALM code for increased readability and reuse. In turbinesFoam, a
turbine is a software object that is composed of actuator line objects, which
themselves are composed of actuator line element objects. Structuring the code
this way allows isolation and reuse of the functionality of individual
components. For example, the actuator line object was written such that is could
be used outside the turbine context to ensure it produces the correct forcing,
without adding the complexity of rotation, other actuator lines, etc. that would
be present in a turbine rotor. The very same actuator line objects can be used
in both axial-flow and cross-flow rotors, without having to copy code from one
to the other.
